models with mice

### 2024-03-06 withmice.Rmd
Mifa for kahan and ecopol nuclear scale

```{r, echo =FALSE}
library(mifa)
library(mice)
library(psych)

@@

mikahan <- mifa(data= kahanall,
                cov_vars = everything(),
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, )

@@

fit <- psych::fa(mikahan$cov_combined,n.obs = nrow(mikahan), nfactors = 2, rotate = "varimax")

print(fit, sort= TRUE, cut= 0.4)

@@

>>>>

## Mifa dor Kahan scale 
```{r, echo =FALSE}
library(mifa)
library(mice)
library(psych)

@@

mikahan <- mifa(data= kahanall,
                cov_vars = everything(),
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 427,)

@@

fit <- psych::fa(mikahan$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(fit, sort= TRUE, cut= 0.4)

@@

#checking imputations: Kahan scale

```{r}
orgscores <- data.frame(kahanefascores)

summary(mikahan)
names(mikahan)

mikahan$mids

complete_data_first <- complete(mikahan$mids, 1)

summary(complete_data_first)

complete_data_2 <- complete(mikahan$mids, 2)

summary(complete_data_2)

complete_data_3 <- complete(mikahan$mids, 3)

summary(complete_data_3)

complete_data_4 <- complete(mikahan$mids, 4)

summary(complete_data_4)

complete_data_5 <- complete(mikahan$mids, 5)

summary(complete_data_5)
```

## Distribution check: kahan Scale

```{r}
# Add an identifier column to each dataset
fct_scores$Dataset <- 'fct_scores'
orgscores$Dataset <- 'orgscores'

# Combine the datasets for plotting
combined_data <- rbind(fct_scores, orgscores)

# Select only necessary columns (assuming 'Index' isn't needed anymore)
combined_data <- combined_data[, c("MR1", "MR2", "Dataset")]

ggplot(combined_data, aes(x = Dataset, y = MR1, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of MR1 for Each Dataset", x = "", y = "MR1 Value") +
  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  theme_minimal()

```
```{r}
ggplot(combined_data, aes(x = Dataset, y = MR2, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of MR2 for Each Dataset with Points", x = "", y = "MR2 Value") +
  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  theme_minimal()

# Mifa for new eco-pol value scale : Nuclear energy

ecopoln <- codedmodule2[, grep("NUCLEAR|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]

miecopol <- mifa(data= ecopoln,
                cov_vars = everything(),
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 429,)

miecopol

fit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(fit2, sort= TRUE, cut= 0.4)

data_imp2 <- mice::complete(mice::mice(ecopoln, 1, print = FALSE))

fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:23], fit2)$scores)

## Checking imputations : Eco-pol scale

orgscores <- data.frame(kahanefascores)

summary(miecopol)
names(miecopol)

miecopol$mids

complete_ecopol_first <- complete(miecopol$mids, 1)

summary(complete_ecopol_first)

complete_ecopol_2 <- complete(miecopol$mids, 2)

summary(complete_ecopol_2)

complete_ecopol_3 <- complete(miecopol$mids, 3)

summary(complete_ecopol_3)

complete_ecopol_4 <- complete(miecopol$mids, 4)

summary(complete_ecopol_4)

complete_ecopol_5 <- complete(miecopol$mids, 5)

summary(complete_ecopol_5)
```
